\LARGE \bf Imposing a Weight Norm Constraint for Neuro–Adaptive Control

### 2025-03-21 manuscript.tex
move macros to template
add more explanation; need to review again to fix typo

\begin{itemize}
    \item $\otimes$ denotes the Kronecker product \cite[Definition 7.1.2]{Bernstein:2009aa}.
    \item $\mv x=[x_i]_{i\in[1,\cdots,n]}\in\R^n$ denotes a vector.
    % \item $\mv x=[x_i]_{i\in[1,\cdots,n]}\in\R^n$ and $
    %     \mm A
    %     := 
    %     [a_{ij}]
    %     _{
    %         i\in[1,\cdots,n],j\in[1,\cdots ,]
    %     }\allowbreak\in\R^{n\times m}
    %     $ denotes a vector and a matrix.
    \item $\myrow_i(\mm A)$ denotes the $i\textsuperscript{th}$ row of the matrix $\mm A\in\R^{n\times m}$. 
    \item $\myvec(\mm A):= [\myrow_1(\mm A^\top)  ,\cdots,\myrow_m(\mm A^\top)  ]^\top   $ for $\mm A\in\R^{n\times m}$.
    % \item $\text{col}_i(A)$ and $\myrow_j(A)$ denote the $i\textsuperscript{th}$ column and $j\textsuperscript{th}$ row of $A\in\R^{n\times m}$, respectively.
    % \item $\myvec(A):= [\text{col}_1(A)^\top  ,\cdots,\text{col}_m(A)^\top  ]^\top   $ for $A\in\R^{n\times m}$.
    \item $\lambda_\text{min}(\mm A)$ denotes the minimum eigenvalue of the matrix $\mm A\in\R^{n\times n}$.
    \item $\mm I_n$ denotes the $n\times n$ identity matrix and $\mm 0_{n\times m}$ denotes the $n\times m$ zero matrix.
\end{itemize}

\section{Introduction}

@@

Consider an uncertain Euler‒Lagrange system modeled as
\begin{equation}
    \mm M\ddq + \mm V_m\dq + \mm F + \mm G + \mv\tau_d
    =
    \mv\tau 
    \label{eq. system dynamics 1}
\end{equation}
where $\q\in \mathbb{R}^n$ and $\mv \tau\in\R^n$ denote the generalized coordinate and the control input, respectively; $\mm M :=\mm M(\q)\in\mathbb{R}^{n\times n}$, $mm V_m:= \mm V_m(\q,\dq)\in\mathbb{R}^{n\times n}$, and $\mm G:=\mm G(\q)\in\mathbb{R}^{n}$ denote the unknown system function matrices; and $\mm F:=\mm F(\dq)\in\mathbb{R}^{n}$ denotes the external force.
Using the user-designed matrices $\mm M_0>0,\mm V_{m0}$ and $\mm G_0$, \eqref{eq. system dynamics 1} can be represented as 
\begin{equation}
    \mm M_0\ddq+\mm V_{m0}\dq+\mm G_0 = \mv \tau + \mv f(\q,\dq,\ddq)
    \label{eq. system dynamics 2}
\end{equation}
where $\mv f(\q,\dq,\ddq) := -(\mm M-\mm M_0)\ddq-(\mm V_m-\mm V_{m0})\dq -(\mm G-\mm G_0) -\mm F$ denotes the residual unknown term.

Hence, the objective of the control design is to make $\q$ track the continuously differentiable desired trajectory $\qd(t):\R\to \R^n$ under the unknown terms $\mv f$.

@@

The backstepping control-based approach is utilized to generate a reference signal $\mv z^*:= -{k_q}\tilde {\q}+\dq_d$ for $\mv {z}:= \dq$, where $\tilde {\q}:= \mv {q} - \qd$ and $k_q\in\R_{>0}$.
The desired stabilizing controller can be designed as follows:
\begin{equation}
    \mv \tau^* = 
    -\mm M_0\cdot ({k_z}\tilde {\mv z})
    + 
        ( 
            -\mm M_0\tilde {\q}+\mm V_{m0}{\mv z}+\mm G_0-\mv f+\mm M_0 \dot {\mv z}^*
        )
    \label{eq. desired control}
\end{equation}
where $\tilde {\mv z}:= \mv z-\mv z^*$ and $k_z\in\R_{>0}$.
Note that the desired controller cannot be realized because of $\mv f$.

To approximate the desired controller, an NN is utilized.
The NN with a single hidden layer is represented as 
\begin{equation}
    \NN({\q_{NN}};\wth):= \wV_1^\top \act(\wV_0^\top {\q_{NN}})
\end{equation}
where ${\q_{NN}}\in\R^{l_0+1}$ denotes the NN input vector, $\wV_i\in\R^{(l_i+1)\times l_{i+1}},\ i\in\{0,1\}$ denotes the weight matrix of the $i\textsuperscript{th}$ layer and $\act:\R^{l_1}\to\R^{l_1+1}$ denotes the activation function layer.
The activation function layer consists of an elementwise nonlinear function $\sigma(\cdot)$ and an augmented $1$ to combine the bias terms in the weight matrix (\ie $\act(\mv x) = \left(\sigma(\mv x_{(1)}),\cdots, \sigma(\mv x_{(l_1)}), 1\right)^\top $).
For further simplicity, let $\wth:=\left(\wth_1^\top ,\wth_0^\top \right)^\top \in\R^{\Xi}$ denote the total weight vector, where $\wth_i:= \myvec(\wV_i)\in\R^{\Xi_i}$ denotes the vectorized weights.
$\Xi_i=(l_i+1)\cdot l_{i+1}$ and $\Xi=\Xi_0+\Xi_1$ denote the number of each layer and total weights, respectively.

Using this NN, the desired controller $\mv \tau^*$ can be approximated by the ideal weight vector $\wth^*$ for a compact subset $\Omega_{NN}\in\R^{l_0+1}$ to $\epsilon$ accuracy such that $\sup_{{\q_{NN}}\in\Omega_{NN}} \allowbreak \norm{\NN({\q_{NN}};\wth^*) - \mv \tau^*}=\epsilon<\infty$ \cite{Cybenko:1989aa}.
The ideal weight vector $\wth^*$ is typically assumed to be bounded.
Then, using the estimated weight vector $\estwth=(\estwth_1^\top ,\estwth_0^\top )^\top $ of $\wth^*=(\wth_1^{*\top},\wth_0^{*\top})^\top $, the desired controller $\mv \tau^*\approx -\NN(\q_{NN};\wth^*)-\epsilon$ can be approximated as follows:
\begin{equation}
    \mv \tau := -\NN({\q_{NN}};\estwth)
    .
    \label{eq. control law}
\end{equation}
For further sections, let $\idealNN:=\NN({\q_{NN}};\idealwth)$ and $\NN^* :=\NN({\idealwV}_0^{\top}{\q_{NN}})$, and let $\estNN:={\NN}({\q_{NN}};\estwth)$, $\estNN :=\NN(\estwV_0^{\top}{\q_{NN}})$ and $\estNN' := \pptfrac{\estNN}{\estwV_0^\top \q_{NN}}$.

Using \eqref{eq. system dynamics 2}, \eqref{eq. desired control}, and \eqref{eq. control law}, the error dynamics can be obtained as the first-order system of augmented error $\mv \xi:=\left(\tilde {\q}^\top ,\tilde {\mv z}^\top\right)^\top \in\R^{2n}$ as follows:
\begin{equation}
    \dot{\mv \xi} 
    = 
    \mm A_\xi{\mv \xi}+\mm B_\xi(\NN^*-\estNN+\mv\epsilon)
\end{equation}
where $\mv \epsilon\in\R^2$ is bounded approximation error and 
\begin{equation}
    \mm A_\xi := 
    \begin{bmatrix}
        -{k_q} \mm I_{n} &\mm I_{n}
        \\
        -\mm I_{n}& -{k_z} \mm I_{n}
    \end{bmatrix}
    ,\ 
    \mm B_\xi := 
    \begin{bmatrix}
        \mm 0_{n\times n}\\\mm M_0^{-1}
    \end{bmatrix}.
\end{equation}

@@

For the boundedness of the weights, weight norm constraints are imposed on the adaptation process such that $c_{\theta_i}=\norm{{\estwth}_i}^2-\bar\theta^2_i,\ i\in[0,1]$.
The control problem can be reformulated into a constrained optimization problem as follows:
\begin{equation}
    \begin{matrix}
        \min_{{\estwth}} \ J(\mv \xi;{\estwth})
        :=
        {1\over 2}
        \mv \xi^\top \mm \Lambda \mv \xi
        \\ \\
        \begin{aligned}
        \text{subject to\;}&c_{j}\le0, \quad j\in\mathcal I 
        = 
        \{\theta_0,\theta_1\}
        ,
        \end{aligned}
    \end{matrix}
\end{equation}
where $\mm \Lambda=\mm \Lambda^\top >0$ denotes the weighting matrix.
In this optimization problem, $\mv \xi$ is considered a predefined parameter.
The corresponding Lagrangian function is defined as
\begin{equation}
    L(
        \mv \xi,
        {\estwth},
        [\lambda_j]_{j\in\mathcal I}
    )
    := 
    J(\mv \xi;{\estwth})
    +
    \textstyle\sum_{j\in\mathcal I} \lambda_jc_j({\estwth})
    .
\end{equation}
% where $\mathcal I=\{j\ \vert \ c_j\ge 0\}$ denotes the active set.
To solve the dual problem $\min_{{\estwth}} \max_{[\lambda_j]_{j\in\mathcal I}}  L$, the adaptation law is derived as follows:
\begin{subequations}
    \begin{align}
            \ddtt {{\estwth}}
            &
            =
            -\alpha 
            \pptfrac{L}{{\estwth}}
            =-\alpha 
            \left(
                \pptfrac{J}{{\estwth}}
                +
                \textstyle\sum_{j\in\mathcal{I}}
                \lambda_j 
                \pptfrac{c_j}{\estwth}
            \right),
        \label{eq. adaptation law th}
            \\
            \ddtt\lambda_j
            & 
            = 
            \beta_j
            \pptfrac{L}{\lambda_j} 
            = 
            \beta_j c_j ,
            \quad\quad\quad\quad      \      
            \forall j\in\mathcal I,
        \label{eq. adaptation law L}
            \\
            \lambda_j 
            & 
            = 
            \max(\lambda_j,0) ,
            \quad\quad\quad\quad\ \ \ \ \ 
            \forall j\in\mathcal I,
        \label{eq. adaptation law L max}
    \end{align}
    \label{eq. adaptation laws}
\end{subequations}
where $\alpha\in\R_{>0}$ and $\beta_j\in\R_{>0}$ denote the adaptation gain and the update rate for each Lagrange multiplier, respectively.
\color{red}
% The Eq.~\eqref{eq. adaptation law L max} is analog to using an active set $\mathcal I=\{j\ \vert \ c_j\ge 0\}$ in constrained optimization theory which excludes terms of satisfied constraints in adaptation law.
\color{black}

Using the chain rule, the gradient of the objective function with respect to the weights (\ie $\pptfrac{J}{\estwth}$) in \eqref{eq. adaptation law th} can be represented as
\begin{equation}
    \pptfrac{J}{\estwth}
    =
    \pptfrac{\mv\xi}{\estwth}^\top 
    \mm \Lambda
    \pptfrac{\mv\xi}{\estwth}
    .
\end{equation}
The calculation of $\pptfrac{J}{\estwth}$ is not straightforward because of the dynamics of $\mv\xi$.
Using the forward sensitivity method presented in \cite{Sengupta:2014aa}, the sensitivity equation can be obtained as follows:
\begin{equation}
    \ddtt{\mm \eta} =
    \mm A_\xi - \mm B_\xi 
    % (\partial \estNN/\partial {\estwth})
    \pptfrac{\estNN}{\estwth}
    ,
    \label{eq. sen eq}
\end{equation}
where ${\mm \eta}:= \pptfrac{\mv\xi}{\estwth}\in\R^{2n\times \Xi}$ denotes the sensitivity of the weights to the augmented error.
The initial value of ${\mm \eta}$ is zero since the initial $\mv\xi$ is independent of the weights.
By decomposing for each layer, the dynamics of ${\mm \eta}_i:= \pptfrac{\mv\xi}{\estwth}_i\in\R^{2n\times \Xi_i}$ can be represented as
\begin{equation}
    \begin{aligned}
        \ddtt{\mm \eta} 
        \!=\!&
        \begin{bmatrix}
            {\mm \eta}_1&{\mm \eta}_0
        \end{bmatrix}'
        \\
        \!=\!&
        \mm A_\xi
        % \begin{bmatrix}
        [
            {\mm \eta}_1
            \ \ 
            {\mm \eta}_0
        ]
        % \end{bmatrix}
        \!-\!
        \mm B_\xi
        % \begin{bmatrix}
        [
            (\mm I_{l_2}\!\otimes\!\estact^\top )
            \ \ 
            \estwV_1^\top \estact'(\mm I_{l_1}\otimes {\q_{NN}}^\top )
        ]
        % \end{bmatrix}
        .
    \end{aligned}
\end{equation}
The calculation of $\pptfrac{\estNN}{\estwth}$ is introduced in \cite{Patil:2022aa}.
In conclusion, the gradient of the objective with respect to the weights can be obtained as $\pptfrac{J}{\estwth} = {\mm \eta}^\top\mm \Lambda\mv\xi$ by simulating the sensitivity equation \eqref{eq. sen eq}.

@@

% For convenience, assume that all the constraints are in the active set without loss of generality.
% If the constraints are not in the active set, the boundedness cannot be guaranteed, but weights will be adapted to reduce the objective function until the constraints are violated.
\color{black}
Without loss of generality, assume that all the constraints. Then, according to \eqref{eq. adaptation law L} and \eqref{eq. adaptation law L max}, all Lagrange multipliers are nonzero.
%If the Lagrange multipliers are not sufficiently generated, the boundedness cannot be guaranteed, but weights will be adapted to reduce the objective function until the constraint violations.
\color{black}

The dynamics of $\mv \xi$ can be represented as
\begin{equation}    
    \ddtt {\mv\xi} = \mm A_\xi\mv \xi +\mm B_\xi
    (
        -\estwV_1^\top \estact+\mv w(t)
    )
\end{equation}
where $\mv w(t):= {\idealwV}_1^{\top}\idealact+\mv \epsilon$ is a lumped residual term, which is bounded as $\norm{\mv  w(t)}\le \bar w< 0$ since $\norm{\idealwth_1}$ and $\norm{\idealact}$ are bounded.
The dynamics of ${\mm \eta}_1$ and ${\estwth}_1$ are represented as
\begin{equation}
    \begin{aligned}
        \ddtt{\mm \eta}_1 =
        & 
        \mm A_\xi {\mm \eta}_1 -\mm B_\xi (\mm I_{l_{2}}\otimes \estact^\top )
        ,
        \\
        \ddtt{{\estwth}}_1 =
        & -\alpha 
        (
            {\mm \eta}_1^\top 
            \mm \Lambda
            \mv\xi
            +
            2\lambda_{\theta_1} {\estwth}_1
        )
        .
    \end{aligned} 
\end{equation}
According to \cite[Chap.~4 T.~1.9]{Desoer:2009aa}, the boundedness of ${\mm \eta}_1$ can be obtained since $\mm A_\xi$ is stable and the residual term $-\mm B_\xi (\mm I_{l_{2}}\otimes \estact^\top )$ is bounded.

>>>>

\begin{itemize}
    \item $\otimes$ denotes the Kronecker product \cite[Definition 7.1.2]{Bernstein:2009aa}.
    \item $\mv x=[x_i]_{i\in\{1,\cdots,n\}}\in\R^n$ denotes a vector.
    % \item $\mv x=[x_i]_{i\in[1,\cdots,n]}\in\R^n$ and $
    %     \mm A
    %     := 
    %     [a_{ij}]
    %     _{
    %         i\in[1,\cdots,n],j\in[1,\cdots ,]
    %     }\allowbreak\in\R^{n\times m}
    %     $ denotes a vector and a matrix.
    \item $\myrow_i(\mm A)$ denotes the $i\textsuperscript{th}$ row of the matrix $\mm A\in\R^{n\times m}$. 
    \item $\myvec(\mm A):= [\myrow_1(\mm A^\top)  ,\cdots,\myrow_m(\mm A^\top)  ]^\top   $ for $\mm A\in\R^{n\times m}$.
    % \item $\text{col}_i(A)$ and $\myrow_j(A)$ denote the $i\textsuperscript{th}$ column and $j\textsuperscript{th}$ row of $A\in\R^{n\times m}$, respectively.
    % \item $\myvec(A):= [\text{col}_1(A)^\top  ,\cdots,\text{col}_m(A)^\top  ]^\top   $ for $A\in\R^{n\times m}$.
    \item $\lambda_\text{min}(\mm A)$ denotes the minimum eigenvalue of the matrix $\mm A\in\R^{n\times n}$.
    \item $\mm I_n$ denotes the $n\times n$ identity matrix and $\mm 0_{n\times m}$ denotes the $n\times m$ zero matrix.
\end{itemize}

\section{Introduction} \label{sec:intro}

@@

Consider an uncertain Euler‒Lagrange system modeled as
\begin{equation}
    \mm M\ddq + \mm V_m\dq + \mm F + \mm G + \mv\tau_d
    =
    \mv\tau 
    \label{eq. system dynamics 1}
\end{equation}
where $\q\in \mathbb{R}^n$ and $\mv \tau\in\R^n$ denote the generalized coordinate and the control input, respectively; $\mm M :=\mm M(\q)\in\mathbb{R}^{n\times n}$, $\mm V_m:= \mm V_m(\q,\dq)\in\mathbb{R}^{n\times n}$, and $\mm G:=\mm G(\q)\in\mathbb{R}^{n}$ denote the unknown system function matrices; and $\mm F:=\mm F(\dq)\in\mathbb{R}^{n}$ denotes the external force.
Using the user-designed matrices $\widehat{\mm M}>0,\widehat{\mm V_m}$ and $\widehat{\mm G}$, \eqref{eq. system dynamics 1} can be represented as 
\begin{equation}
    \widehat{\mm M}\ddq+\widehat{\mm V_m}\dq+\widehat{\mm G} = \mv \tau + \mv f(\q,\dq,\ddq)
    \label{eq. system dynamics 2}
\end{equation}
where $\mv f(\q,\dq,\ddq) := -(\mm M-\widehat{\mm M})\ddq-(\mm V_m-\widehat{\mm V_m})\dq -(\mm G-\widehat{\mm G}) -\mm F$ denotes the residual unknown term.

Hence, the objective of the control design is to make $\q$ track the continuously differentiable desired trajectory $\qd:=\qd(t):\R\to \R^n$ under the unknown terms $\mv f:=\mv f(\q,\dq,\ddq)$.

@@

The backstepping control-based approach is utilized to generate a reference signal $\mv z^*:= -{k_q}\tilde {\q}+\dq_d$ for $\mv {z}:= \dq$, where $\tilde {\q}:= \mv {q} - \qd$ and $k_q\in\R_{>0}$.
The desired stabilizing controller can be designed as follows:
\begin{equation}
    \mv \tau^* = 
    -\widehat{\mm M}\cdot ({k_z}\tilde {\mv z})
    + 
        ( 
            -\widehat{\mm M}\tilde {\q}
            +
            \widehat{\mm V_m}{\mv z}
            +
            \widehat{\mm G}
            -
            \mv f
            +
            \widehat{\mm M} \dot {\mv z}^*
        )
    \label{eq. desired control}
\end{equation}
where $\tilde {\mv z}:= \mv z-\mv z^*$ and $k_z\in\R_{>0}$.
Note that the desired controller cannot be realized because of $\mv f$.

To approximate the desired controller, an NN is utilized.
\MSRY{
    Even though the DNNs have a higher approximation capability than the SHLNNs \cite{Rolnick:2017aa}, here, the SHLNN is utilized for simplicity and low computational complexity.
}
The NN with a single hidden layer is represented as 
\begin{equation}
    \NN({\q_{NN}};\wth):= \wV_1^\top \act(\wV_0^\top {\q_{NN}})
\end{equation}
where ${\q_{NN}}\in\R^{l_0+1}$ denotes the NN input vector, $\wV_i\in\R^{(l_i+1)\times l_{i+1}},\ i\in\{0,1\}$ denotes the weight matrix of the $i\textsuperscript{th}$ layer and $\act:\R^{l_1}\to\R^{l_1+1}$ denotes the activation function layer.
The activation function layer consists of an elementwise nonlinear function $\sigma(\cdot)$ and an augmented $1$ to combine the bias terms in the weight matrix (\ie $\act(\mv x) = \left(\sigma(\mv x_{(1)}),\cdots, \sigma(\mv x_{(l_1)}), 1\right)^\top $).
For further simplicity, let $\wth_i:= \myvec(\wV_i)\in\R^{\Xi_i}$ denotes the vectorized weights and $\wth:=(\wth_1^\top ,\wth_0^\top )^\top \in\R^{\Xi}$ denote the total weight vector, where $\Xi_i=(l_i+1)\cdot l_{i+1}$ and $\Xi=\Xi_0+\Xi_1$ denote the number of each layer and total weights, respectively.

Using this NN, the desired controller $\mv \tau^*$ can be approximated by the ideal weight vector $\wth^*$ for a compact subset $\Omega_{NN}\in\R^{l_0+1}$ to $\epsilon$ accuracy such that $\sup_{{\q_{NN}}\in\Omega_{NN}} \allowbreak \norm{\NN({\q_{NN}};\wth^*) - \mv \tau^*}=\epsilon<\infty$ \cite{Cybenko:1989aa}.
The ideal weight vector $\wth^*$ is typically assumed to be bounded.
Then, using the estimated weight vector $\estwth=(\estwth_1^\top ,\estwth_0^\top )^\top $ of $\wth^*=(\wth_1^{*\top},\wth_0^{*\top})^\top $, the desired controller $\mv \tau^*\approx -\NN(\q_{NN};\wth^*)-\mv\epsilon$ with bounded approximation error $\mv \epsilon\in\R^2$, can be approximated as follows:
\begin{equation}
    \mv \tau := -\NN({\q_{NN}};\estwth)
    .
    \label{eq. control law}
\end{equation}
For further sections, let $\idealNN:=\NN({\q_{NN}};\idealwth)$ and $\idealact :=\act({\idealwV}_0^{\top}{\q_{NN}})$, and let $\estNN:={\NN}({\q_{NN}};\estwth)$, $\estact :=\act(\estwV_0^{\top}{\q_{NN}})$ and $\estact' := \pptfrac{\estact}{\estwV_0^\top \q_{NN}}$.

Using \eqref{eq. system dynamics 2}, \eqref{eq. desired control}, and \eqref{eq. control law}, the error dynamics can be obtained as the first-order system of augmented error $\mv \xi:=(\tilde {\q}^\top ,\tilde {\mv z}^\top)^\top \in\R^{2n}$ as follows:
\begin{equation}
    \dot{\mv \xi} 
    = 
    \mm A_\xi{\mv \xi}+\mm B_\xi(\NN^*-\estNN+\mv\epsilon)
\end{equation}
and 
\begin{equation}
    \mm A_\xi := 
    \begin{bmatrix}
        -{k_q} \mm I_{n} &\mm I_{n}
        \\
        -\mm I_{n}& -{k_z} \mm I_{n}
    \end{bmatrix}
    ,\ 
    \mm B_\xi := 
    \begin{bmatrix}
        \mm 0_{n\times n}\\\widehat{\mm M}^{-1}
    \end{bmatrix}.
\end{equation}

@@

\MSRY{
    As discussed in Section \ref{sec:intro}, the boundedness of the weights should be addressed to prevent excessively large control inputs and system instability.
}
For the boundedness of the weights, weight norm constraints are imposed on the adaptation process such that $c_{\theta_i}=\norm{{\estwth}_i}^2-\bar\theta^2_i,\ i\in\{0,1\}$.
The control problem can be reformulated into a constrained optimization problem as follows:
\begin{equation}
    \begin{matrix}
        \min_{{\estwth}} \ J(\mv \xi;{\estwth})
        :=
        \tfrac{1}{2}
        \mv \xi^\top \mm \Lambda \mv \xi
        \\ \\
        \begin{aligned}
        \text{subject to\;}&c_{j}\le0, \quad j\in\mathcal I 
        = 
        \{\theta_0,\theta_1\}
        ,
        \end{aligned}
    \end{matrix}
\end{equation}
where $\mm \Lambda=\mm \Lambda^\top >0$ denotes the weighting matrix.
In this optimization problem, $\mv \xi$ is considered a predefined parameter.
The corresponding Lagrangian function is defined as
\begin{equation}
    L(
        \mv \xi,
        {\estwth},
        [\lambda_j]_{j\in\mathcal I}
    )
    := 
    J(\mv \xi;{\estwth})
    +
    \textstyle\sum_{j\in\mathcal I} \lambda_jc_j({\estwth})
    .
\end{equation}
% where $\mathcal I=\{j\ \vert \ c_j\ge 0\}$ denotes the active set.
To solve the dual problem $\min_{{\estwth}} \max_{[\lambda_j]_{j\in\mathcal I}}  L$, the adaptation law is derived as follows:
\begin{subequations}
    \begin{align}
            \ddtt {{\estwth}}
            &
            =
            -\alpha 
            \pptfrac{L}{{\estwth}}
            =-\alpha 
            \left(
                \pptfrac{J}{{\estwth}}
                +
                \textstyle\sum_{j\in\mathcal{I}}
                \lambda_j 
                \pptfrac{c_j}{\estwth}
            \right),
        \label{eq. adaptation law th}
            \\
            \ddtt\lambda_j
            & 
            = 
            \beta_j
            \pptfrac{L}{\lambda_j} 
            = 
            \beta_j c_j ,
            \quad\quad\quad\quad      \      
            \forall j\in\mathcal I,
        \label{eq. adaptation law L}
            \\
            \lambda_j 
            & 
            = 
            \max(\lambda_j,0) ,
        \label{eq. adaptation law L max}
    \end{align}
    \label{eq. adaptation laws}
\end{subequations}
where arguments of $L$ are suppressed for brevity, and $\alpha\in\R_{>0}$ and $\beta_j\in\R_{>0}$ denote the adaptation gain and the update rate for each Lagrange multiplier, respectively.
\color{red}
% The Eq.~\eqref{eq. adaptation law L max} is analog to using an active set $\mathcal I=\{j\ \vert \ c_j\ge 0\}$ in constrained optimization theory which excludes terms of satisfied constraints in adaptation law.
\color{black}

Using the chain rule, the gradient of the objective function with respect to the weights (\ie $\pptfrac{J}{\estwth}$) in \eqref{eq. adaptation law th} can be represented as
\begin{equation}
    \pptfrac{J}{\estwth}
    =
    \pptfrac{\mv\xi}{\estwth}^\top 
    \mm \Lambda
    \mv\xi
    .
\end{equation}
The calculation of $\pptfrac{J}{\estwth}$ is not straightforward because of the dynamics of $\mv\xi$.
Using the forward sensitivity method presented in \cite{Sengupta:2014aa}, the sensitivity equation can be obtained as follows:
\begin{equation}
    \ddtt{\mm \eta} =
    \mm A_\xi \mm\eta
    - \mm B_\xi 
    % (\partial \estNN/\partial {\estwth})
    \pptfrac{\estNN}{\estwth}
    ,
    \label{eq. sen eq}
\end{equation}
where ${\mm \eta}:= \pptfrac{\mv\xi}{\estwth}\in\R^{2n\times \Xi}$ denotes the sensitivity of the weights to the augmented error.
The initial value of ${\mm \eta}$ is zero since the initial $\mv\xi$ is independent of the weights.
By decomposing for each layer, the dynamics of ${\mm \eta}_i:= \pptfrac{\mv\xi}{\estwth}_i\in\R^{2n\times \Xi_i}$ can be represented as
\begin{equation}
    \begin{aligned}
        \ddtt{\mm \eta} 
        \!=\!&
        \begin{bmatrix}
            {\mm \eta}_1&{\mm \eta}_0
        \end{bmatrix}'
        \\
        \!=\!&
        \mm A_\xi
        % \begin{bmatrix}
        [
            {\mm \eta}_1
            \ \ 
            {\mm \eta}_0
        ]
        % \end{bmatrix}
        \!-\!
        \mm B_\xi
        % \begin{bmatrix}
        [
            (\mm I_{l_2}\!\otimes\!\estact^\top )
            \ \ 
            \estwV_1^\top \estact'(\mm I_{l_1}\otimes {\q_{NN}}^\top )
        ]
        % \end{bmatrix}
        .
    \end{aligned}
\end{equation}
The calculation of $\pptfrac{\estNN}{\estwth}$ is introduced in \cite{Patil:2022aa}.
In conclusion, the gradient of the objective with respect to the weights can be obtained as $\pptfrac{J}{\estwth} = {\mm \eta}^\top\mm \Lambda\mv\xi$ by simulating the sensitivity equation \eqref{eq. sen eq}.

@@

% For convenience, assume that all the constraints are in the active set without loss of generality.
% If the constraints are not in the active set, the boundedness cannot be guaranteed, but weights will be adapted to reduce the objective function until the constraints are violated.
\color{black}
Without loss of generality, assume that all the constraints are violated. 
Then, according to \eqref{eq. adaptation law L} and \eqref{eq. adaptation law L max}, all Lagrange multipliers are nonzero.
%If the Lagrange multipliers are not sufficiently generated, the boundedness cannot be guaranteed, but weights will be adapted to reduce the objective function until the constraint violations.
\color{black}

The dynamics of $\mv \xi$ can be represented as
\begin{equation}    
    \ddtt {\mv\xi} = \mm A_\xi\mv \xi +\mm B_\xi
    (
        -\estwV_1^\top \estact+\mv w(t)
    )
\end{equation}
where $\mv w(t):= {\idealwV}_1^{\top}\idealact+\mv \epsilon$ is a lumped residual term, which is bounded as $\norm{\mv  w(t)}\le \bar w< 0$ since $\norm{\idealwth_1},\norm{\idealact}$ and $\norm{\mv\epsilon}$ are bounded.
The dynamics of ${\mm \eta}_1$ and ${\estwth}_1$ are represented as
\begin{equation}
    \begin{aligned}
        \ddtt{\mm \eta}_1 =
        & 
        \mm A_\xi {\mm \eta}_1 -\mm B_\xi (\mm I_{l_{2}}\otimes \estact^\top )
        ,
        \\
        \ddtt{{\estwth}}_1 =
        & -\alpha 
        (
            {\mm \eta}_1^\top 
            \mm \Lambda
            \mv\xi
            +
            2\lambda_{\theta_1} {\estwth}_1
        )
        .
    \end{aligned} 
\end{equation}
According to \cite[Chap.~4 T.~1.9]{Desoer:2009aa}, the boundedness of ${\mm \eta}_1$ can be obtained since $\mm A_\xi$ is stable and the residual term $-\mm B_\xi (\mm I_{l_{2}}\otimes \estact^\top )$ is bounded.

Define the Lyapunov function $V_1:=\tfrac{1}{2}\mv\xi^\top \mm P\mv\xi+\tfrac{1}{2\alpha}{\estwth}_1^\top {\estwth}_1$, with the Lyapunov equation $\mm A_\xi^\top \mm P+\mm P\mm A_\xi=-\mm Q$, where $\mm A_\xi<0,\mm P=\mm P^\top >0$, and $\mm Q>0$.
Using a proposition $\estwV_1^\top \estact = \myvec(\estwV_1^\top \estact)=\myvec(\estact^\top \estwV_1) = (\mm I_{l_2}\otimes {\estact}^\top )\myvec(\estwV_1)=(\mm I_{l_2}\otimes \estact^\top ){\estwth}_1$ \cite[Proposition~(7.1.9)]{Bernstein:2009aa}, the time derivative of $V_1$ is
\begin{equation}
    \begin{aligned}
        \ddtt \! {V}_1 
        \!=\!& 
        \tfrac{1}{2}
        \mv \xi^\top 
            (
                \mm A_\xi^\top \mm P+\mm P\mm A_\xi
            )
        \mv \xi
        \!+\!
        \mv \xi^\top \mm P (
            \!-\!\mm B_\xi\estwV_1^\top \estact +\mm B_\xi \mv w(t) 
        )\\
        &
        -{\estwth}_1^\top 
        \!
        (
            {\mm \eta}_1^\top \mm \Lambda \xi+2\lambda_{\theta_1} {\estwth}_1 
        )
        \\
        =& 
        -\tfrac{1}{2}
        \mv \xi^\top \mm Q\mv \xi 
        -
        \mv \xi^\top \mm P\mm B_\xi(\mm I_{l_2}\otimes \estact^\top ){\estwth}_1 
        +\mv \xi^\top \mv \Delta
        \\
        &
        -{\estwth}_1^\top {\mm \eta}_1^\top \mm \Lambda\mv \xi
        -2\lambda_{\theta_1} {\estwth}_1^\top {\estwth}_1
        \\
        \le&
        -
        \tfrac{1}{2}
        \lambda_\text{min}(\mm Q)\norm{\mv \xi} ^2
        +\bar\Delta \norm{\mv \xi}
        +\bar M\norm{\mv \xi} \norm{{\estwth}_1}
        \\
        &
        -2\lambda_{\theta_1}
        \norm{{\estwth}_1}^2
        \\
        \le& 
        (
            -\tfrac{1}{2}\lambda_\text{min}(\mm Q)
            +{\tfrac{\bar M}{2}}
        )
        \norm{\mv \xi}^2 +\bar\Delta \norm{\mv \xi}
        \\
        &+ 
        (
        -2\lambda_{\theta_1} 
        +\tfrac{\bar M}{2}
        )
        \norm{\tilde{\wth}_1}^2 
        ,
        \end{aligned}
        \label{eq. lya 1}
\end{equation}
where $\mv \Delta:= \mm P\mm B_\xi \mv w(t)$ and $\mm M:= -\mm P\mm B_\xi(\mm I_{l_2}\otimes \estact^\top )-\mm \Lambda{\mm \eta}_1$ are bounded such that $\norm{\mv \Delta}\le\bar\Delta<\infty$ and $\norm{\mm M}_F\le \bar M< \infty$, respectively.

By defining $\mm P=\mm I_n$, the eigenvalues of $\mm Q=-\mm A_\xi^\top -\mm A_\xi$ are $2k_q$ and $2k_z$, since $\mm A_\xi$ is a skew-symmetric matrix except for the diagonal entries.
According to \eqref{eq. lya 1}, if $k_q$ and $k_z$ are provided that
\begin{equation}
    \text{min}(k_q,k_z)>\tfrac{\bar M}{2}
    ,
    \label{eq. ctrl stable condition}
\end{equation}
and if $\lambda_{\theta_1}$ is increased sufficiently large such that $2\lambda_{\theta_1}>\tfrac{\bar M}{2}$, due to the violation of $c_{\theta_1}$, the tracking error is bounded in
\begin{equation}
    \Theta_\xi := 
    \left\{
        \mv\xi\mid
        \norm{\mv\xi}
        \le  
        \tfrac{
            2\bar \Delta
        }{
            \lambda _\text{min}(\mm Q)-{\bar M}
        } 
    \right\}
    ,
\end{equation}
and the weight estimation $\estwth_1$ is bounded in
\begin{equation}
    \Theta_{{\theta}_1} := 
    \left\{ 
        {\estwth_1} 
        \mid
        \norm{\estwth_1}
        \le  
        \bar\theta_1
    \right\}
    .
\end{equation}
The Lagrange multiplier $\lambda_{\theta_1}$ is also bounded since the $\lambda_{\theta_1}$ update stops once ${\estwth}_1$ approaches the compact set $\Theta_{{\theta}_1}$, satisfying the constraint $c_{\theta_1}$.
